Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-29 writing/DraftExposurePaper/DraftExposurePaper.Rmd
add some code

```{r echo = FALSE, fig.height = 4, fig.width = 6}
allison_gauge <- read.csv("MWR_gauge_rain_data/allison_mwr.csv")
allison_nldas <- county_rain(counties = unique(allison_gauge$fips),
                             start_year = 2001, end_year = 2001,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
allison_nldas <- allison_nldas %>%
        filter(storm_id == "Allison-2001")
allison_gauge$fips <- as.character(allison_gauge$fips)
compare_rain <- right_join(allison_nldas, allison_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```

>>>>

```{r echo = FALSE, fig.height = 4, fig.width = 6}
#allison_gauge <- read.csv("~/Documents/hurricaneexposure/writing/DraftExposurePaper/MWR_gauge_rain_data/allison_mwr.csv")
allison_gauge <- read.csv("MWR_gauge_rain_data/allison_mwr.csv")
allison_nldas <- county_rain(counties = unique(allison_gauge$fips),
                             start_year = 2001, end_year = 2001,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
allison_nldas <- allison_nldas %>%
        filter(storm_id == "Allison-2001")
allison_gauge$fips <- as.character(allison_gauge$fips)
compare_rain <- right_join(allison_nldas, allison_gauge, by = "fips")
#alex_nldas <- as.data.table(alex_nldas)
#alex_gauge <- as.data.table(alex_gauge)
#compare_rain <- left_join(alex_nldas, alex_gauge, by = "fips")
a <- ggplot(compare_rain, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
a
```
